The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-04-01 albatros_paper.tex
HCC updated albatros pathfinder glamor shot, more section 2 text updates

{\bf Write text here about the overall final configuration.  Describe
  the site, show synthesized beam, discuss high level system
  requirements (power, data storage, etc).  Include deployment
  schedule and introduce 2-element pathfinder in the following
  section.}

@@

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/ALBATROS-EGG.PNG}
    \caption{The two-element \albatros\ pathfinder on Marion Island.
      Two dual-polarization LWA antennas are separated by roughly
      110~m on an east--west baseline. Coaxial cables connect the
      antennas to an orange shipping container that houses the readout
      electronics and serves as our ``command module.''}
    \label{Fig:albatros2}
  \end{center}
\end{figure}

@@

\section{Pathfinder Installations and Preliminary Observations}
\subsection{Marion Island}
 Marion Island is a research location managed by the South African National Antarctic Programme (SANAP) and is located at \ang{46;54;45}S, \ang{37;44;37}E on the sub-antarctic of the Southern Indian Ocean. It is $\approx$\SI{2000}{\kilo\metre} from the nearest continental landmass which is also an approximate maximum distance for meteor scattering. The island has an area of \SI{290}{\kilo\metre\squared} and is only accessible once in April of every year by means of the S. A. Agulhas vessel owned by the Department of Environmental Affairs.

@@

\section{Future Work}

\begin{figure}[h]
	\centering
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{Figures/site.PNG}
		\caption{Marion Island huts which are potential stations for the ALBATROS. The ring-like pattern is appropriate for imaging and produces a FWHM synthesized beam of 8' at 5 MHz.}
		\label{Fig:Marion}
	\end{subfigure}%
	~~~			
	\begin{subfigure}[t]{0.5\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{Figures/beam.png}
		\caption{Omnidirectional, dome shaped beam pattern which promises an improved resolution over the existing experiments to date.}
		\label{Fig:beam}
	\end{subfigure}
	\caption{Potential stations and a beam encouraging enough to implement ALBATROS experiment}
	\label{Fig:10}
\end{figure}

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=0.5\linewidth]{Figures/site.PNG}
    \caption{{\bf UPDATE THIS FIGURE} Marion Island huts which are
      potential stations for the ALBATROS. The ring-like pattern is
      appropriate for imaging and produces a FWHM synthesized beam of
      8' at 5 MHz.}
    \label{Fig:marion}
  \end{center}
\end{figure}

% Write text here about the overall final configuration.  Describe the
% site, show synthesized beam, discuss high level system requirements
% (power, data storage, etc).  Include deployment schedule and introduce
% 2-element pathfinder in the following section.

The primary requirements that drive the design for a low-frequency
imaging experiment are 1) desired resolution, 2) low RFI, and 3) quiet
ionospheric conditions.  As a benchmark, an interferometer operating
at 30~MHz requires order-of-magnitude baseline lengths of $\sim 1$~km
to achieve a resolution of $\sim 1$\degree.  This length scales
inversely with frequency, and therefore $\sim 10$-km lengths are
required at few-MHz frequencies in order to improve upon the
resolutions achieved to date.  {\bf More words here about RFI and
  ionosphere.}

@@

Marion Island is a research location managed by the South African
National Antarctic Programme (SANAP) and is located at
\ang{46;54;45}S, \ang{37;44;37}E on the sub-antarctic of the Southern
Indian Ocean. It is $\approx$\SI{2000}{\kilo\metre} from the nearest
continental landmass which is also an approximate maximum distance
for meteor scattering. The island has an area of
\SI{290}{\kilo\metre\squared} and is only accessible once in April of
every year by means of the S. A. Agulhas vessel owned by the
Department of Environmental Affairs.

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=0.7\linewidth]{Figures/albatros_2elem/albatros_2elem.pdf}
    \caption{The two-element \albatros\ pathfinder on Marion Island.
      Two dual-polarization LWA antennas are separated by roughly
      110~m on an east--west baseline. Coaxial cables connect the
      antennas to an orange shipping container that houses the readout
      electronics and serves as our ``command module.''}
    \label{Fig:albatros2}
  \end{center}
\end{figure}

@@

\section{Pathfinder Installations and Preliminary Observations}

@@

% \section{Future Work}
